### 2021-02-26 rad-icfp-2021/simplediff.tex
minor

>>>>

We are now able to present a simple transformation for purely functional reverse-mode on UNF.
This transformation is somehow straightforward as some of the work was put into the design of UNF.
Our main takeaway for this paper is that reverse-mode is complicated beause there is a lot happening in the same time. 
But by decoupling the problems, it becomes muche easier. UNF is somehow dealing with the inherent type-dependency of reverse-mode.
Then the macro $\Dsynrevsymbol$ adds Jacobians. It allows to compute gradients in a compositional way.
Finally, we'll see in the next section how to compile back to a normal language and optimise our transformation to get efficiency.

The differentiation macro is given in Figure~\ref{fig:diff_macro}.
